ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
updating code in Fig. 2
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

\begin{figure} [htb]
\centering
\begin{minipage}{8.5cm}
\begin{lstlisting}
#include <...>
#define BLOCKS 1
#define THREADS 2
__global__ void kernel(int *A) {
	A[threadIdx.x + 1] = threadIdx.x;
}
int main(){
	int *a;
	int *dev_a;
	int size = THREADS*sizeof(int);
	a = (int*)malloc(size);
	cudaMalloc((void**)&dev_a, size);
	for (int i = 0; i < THREADS; i++)
		a[i] = 0;
	cudaMemcpy(dev_a, a, size, cudaMemcpyHostToDevice);
	// kernel<<<BLOCKS,THREADS>>>(dev_a);
	ESBMC_verify_kernel(kernel, BLOCKS, THREADS, dev_a);
	for (int i = 0; i < THREADS; i++)
		assert(a[i]==i);	
	cudaFree(dev_a);
	return 0;
}
\end{lstlisting}
\end{minipage}
\caption{Illustrative CUDA code example.}
\label{fig:illustrative-example}
\end{figure}

>>>>

\begin{figure} [htb]
\centering
\begin{minipage}{8.5cm}
\begin{lstlisting}
#include <...>
#define BLOCKS 1
#define THREADS 2

__global__ void kernel(int *A) {
	A[threadIdx.x + 1] = threadIdx.x;
}

int main(){
	int *a;
	int *dev_a;
	int size = THREADS*sizeof(int);
	a = (int*)malloc(size);
	cudaMalloc((void**)&dev_a, size);
	for (int i = 0; i < THREADS; i++)
		a[i] = 0;
	cudaMemcpy(dev_a, a, size, cudaMemcpyHostToDevice);
	// kernel<<<BLOCKS,THREADS>>>(dev_a);
	ESBMC_verify_kernel(kernel, BLOCKS, THREADS, dev_a);
	cudaMemcpy(a, dev_a , size , cudaMemcpyDeviceToHost);
	for (int i = 0; i < THREADS; i++)
		assert(a[i]==i);	
	cudaFree(dev_a);
	free(a);
	return 0;
}
\end{lstlisting}
\end{minipage}
\caption{Illustrative CUDA code example.}
\label{fig:illustrative-example}
\end{figure}
